---
title: "Data Acquisition and Management Week 3 Assignment"
author: "Chun San Yip"
date: "2019/02/23"
output: html_document
---

Overview:
The assignment for this week is related to Regular Expressions.

Load the Tidyverse packages.
```{r load-packages, message = FALSE}
library(tidyverse)
```

Read majors data from CSV
```{r}
theUrl <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
majors <- read.csv(file=theUrl, header=TRUE, sep=",", stringsAsFactors = FALSE)
head(majors)
```

Identifies the majors that contain either "DATA" or "STATISTICS"
```{r}
str_view(majors$Major, "DATA|STATISTICS", match=TRUE)
```

Transform data from one format to another format
```{r}
a <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'
aa <- str_c(unlist(str_extract_all(a, "\"([a-z]+)\\s*([a-z]+)*\"")), collapse=", ")
cat("c(", aa, ")")
```


#3 Describe, in words, what these expressions will match:

A. (.)\1\1 - (.) is any character except newline. The backreference \1 references the first capturing group (.). The second \1 also references the first capturing group(.)
```{r}
regex_expr = '(.)\\1\\1'
test_cases = c('aaa','"aaa"', "aba")
str_view_all(test_cases, regex_expr)
```
 
B. "(.)(.)\\2\\1" - It is a string that defines a regular expression. 2 x (.) are any 2 characters except newline. \\2 refers to the second (.) while \\1 referes to the first (.) from the left. 
```{r}
regex_expr = '"(.)(.)\\2\\1"'
test_cases = c('anna','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```

C. (..)\1 - (..) is any 2 characters except newline. The backreference \1 references the first capturing group (..)
```{r}
regex_expr = '(..)\\1'
test_cases = c('abab', 'anna','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```
    
D. "(.).\\1.\\1"- It is a string that defines a regular expression. There are 5 (any) characters altogether. Both \\1 are refering to the first capturing group (.). - 
```{r}
regex_expr = "(.).\\1.\\1"
test_cases = c('abaca', 'abab', 'anna','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```

E. "(.)(.)(.).*\\3\\2\\1" - 3 capturing group (.) of any character, 1 any character, 	* represents 0 or more of any character , \\3 references the third (.), \\2 references the second (.) and \\1 references the first (.).
```{r}
regex_expr = "(.)(.)(.).*\\3\\2\\1"
test_cases = c('abcdefgcba', 'abab', 'anna','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```

#4 Construct regular expressions to match words that:

A. Start and end with the same character. - "^(.).*\\1$"
```{r}
regex_expr = "^(.).*\\1$"
test_cases = c('abab', 'anna','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```

B. Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.) - 
"(..).*\\1"
```{r}
regex_expr = "(..).*\\1"
test_cases = c('abab', 'church','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```

C. Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)- "(.).*\\1.*\\1.*"
```{r}
regex_expr = "(.).*\\1.*\\1.*"
test_cases = c('ababab', 'church','eleven','"anna"', 'Maria','""','"able was I ere I saw hannah"')
str_view_all(test_cases, regex_expr)
```
