---
title: "Data Acquisition and Management Week 3 Assignment"
author: "Chun San Yip"
date: "2019/02/15"
output: html_document
---

Overview:
The assignment for this week is related to Regular Expressions.

Load the dplyr packages.
```{r load-packages, message = FALSE}
library(tidyverse)
```

Read majors data from CSV - something is wrong with VPN from China and I can only download the file to work on it.
```{r}
theUrl <- "C:/data/majors-list.csv"
majors <- read.csv(file=theUrl, header=TRUE, sep=",", stringsAsFactors = FALSE)
head(majors)
```

Identifies the majors that contain either "DATA" or "STATISTICS"
```{r}
str_view(majors$Major, "DATA|STATISTICS", match=TRUE)
```

Transform Data from one format to a vector function format (can't figure out the right answer)
```{r}
a <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'
aex <- str_extract_all(a, "\".*\"")
aex
```

#3 Describe, in words, what these expressions will match:

A. (.)\1\1 - (.) is any character except newline. The backreference \1 references the first capturing group (.) twice.
 
B. "(.)(.)\\2\\1" - It is a string that defines a regular expression. (.) is any character except newline. \\2 refers to the second (.) while \\1 referes to the first (.) from the left. 

C. (..)\1 - (..) is any 2 characters except newline. The backreference \1 references the first capturing group (..)
    
D. "(.).\\1.\\1"- It is a string that defines a regular expression. There are 5 (any) characters altogether. Both \\1 are refering to the first group (.). - 

E. "(.)(.)(.).*\\3\\2\\1" - 3 capturing group of any character, 1 any character, 	* represents 0 or more of . , \\3 references the third (.), \\2 references the second (.) and \\ references the first (.).

#4 Construct regular expressions to match words that:

A. Start and end with the same character. - "^(.).*\\1$"

B. Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.) - 
"(..).*\\1"

C. Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)- "(.).*\\1.*\\1.*\\1"

